---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rphido

<!-- badges: start -->
<!-- badges: end -->

The goal of `rphido` is to make it easier for Public Health Staff to
access and use data to improve public health

## Installation

You can install the development version of rphido from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lockhartandrewj/rphido")
```


## Usage

The first function `rphido` has is `str_split_one`.

The `str_split_one` function splits strings into character vectors **not** lists.

A fairly common task when dealing with strings is the need to split a 
single string into many parts.

This is what `base::strsplit()` and `stringr::str_split()` do.

```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```

Notice how the return value is a **list** of length one, where the first element
holds the character vector of parts.
Often the shape of this output is inconvenient, i.e. we want the un-listed version.

That's exactly what `rphido::str_split_one()` does.

```{r}
library(rphido)

str_split_one(x, pattern = ",")
```

Use `str_split_one()` when the input is known to be a single string.
For safety, it will error if its input is already a vector or list that has 
length greater than one.

`str_split_one()` is built on `stringr::str_split()`, so you can use its
`n` argument and stringr's general interface for describing the `pattern`
to be matched.

```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```
